### 2012-12-04 inst/examples/policycosts/figure4.Rmd
figure4 set up for run on farm

``` {r libraries, include=FALSE}
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

@@

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.01               # economic discounting rate
OptTime <- 100              # stopping time
gridsize <- 100              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

@@

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- lapply(penaltyfns, function(penalty){
  sfLapply(c2, function(c2)
      optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                   profit, delta, reward, penalty = penalty(c2))
  )
})
````

>>>>

``` {r libraries, include=FALSE}
rm(list=ls())
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
```

@@

```{r setup}
seed <- 123                 # Random seed (replicable results)
delta <- 0.05               # economic discounting rate
OptTime <- 20               # stopping time
gridsize <- 50              # grid size for fish stock and harvest rate (discretized population)
sigma_g <- 0.2              # Noise in population growth
reward <- 0                 # bonus for satisfying the boundary condition
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1         # No measurement noise, 
z_i <- function() 1         # No implemenation noise
f <- BevHolt                # Select the state equation
pars <- c(1.5, 0.05)        # parameters for the state equation
K <- (pars[1] - 1)/pars[2]  # Carrying capacity (for reference 
xT <- 0                     # boundary conditions
x0 <- K
x_grid <- seq(0.01, 1.2 * K, length = gridsize)  
h_grid <- seq(0.01, 0.8 * K, length = gridsize)  
````

@@

``` {r  bigloop, dependson=c("setup", "reed", "fees")}
policies <- lapply(penaltyfns, function(penalty){
  sfLapply(c2, function(c2){
      policy <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                   profit, delta, reward, penalty = penalty(c2))
      }
  )
})
````
